---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.  -->



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# denverweed
<!-- badges: start -->
<!-- badges: end -->

The goal of XXX is to ...

## Installation

The development version of denverweed is available from [GitHub](https://github.com/) with:
```{r}
#install.packages("devtools")
#devtools::install_github("Reed-Math241/pkgGrpm")
```



## About the data 

The Data were collected and made available by the City of Denver Open Data Catalog.

the denverweed package contains two datasets. 
```{r}
library(pkgGrpm)
data(package = 'pkgGrpm')
```


It contains the dataset `weed`, which contains 4 variables and 90 observations:

```{r}
head(weed)
```

It also contains `weed_wider`, a pivoted, untidy version of `weed` which may be useful for certain graphs, containing 4 variables and 45 observations

```{r}
head(weed_wider)
```

## Example

gross sales by year, faceted by medical or retail 
```{r}
library(tidyverse)

ggplot(weed, aes(x = YEAR, y = GROSS_SALES)) + 
  geom_bar(stat = 'identity') +
  facet_wrap(~GROSS_SALES_TYPE) +
  scale_y_continuous(labels = scales::comma) + 
  ylab("Gross Sales ($)") + 
  xlab("Year")+
  theme_bw()
```

gross sales by month, faceted by year 
```{r}

ggplot(weed, aes(x = MONTH, y = GROSS_SALES)) + 
  geom_bar(stat = 'identity') +
  facet_wrap(~YEAR) +
  scale_y_continuous(labels = scales::comma) +
  ylab("Gross Sales ($)") + 
  xlab("Year") +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90))

```

gross sales by month, faceted by year and retail/medical

```{r}
ggplot(weed, aes(x = MONTH, y = GROSS_SALES)) + 
  geom_bar(stat = 'identity') +
  facet_grid(GROSS_SALES_TYPE ~ YEAR) +
  scale_y_continuous(labels = scales::comma) + 
  ylab("Gross Sales ($)") + 
  xlab("Year") +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90))


```

finally, a use for `weed_wider` in a scatterplot of medical vs retail sales, by year


```{r}

ggplot(weed_wider, aes(x = `Medical Total Gross Sales`, y = `Retail Total Gross Sales`, color = YEAR)) +
  geom_point()+
  scale_y_continuous(labels = scales::comma)+
  theme_bw()
```


